### 2018-05-27 write-up/conclusion.tex
Finish Introduction

I showed that this implementation was \textbf{more memory-efficient} than one
written using a high-level linear-algebra libraries and performed just as
\textbf{predictably} as one written using a low-level linear-algebra library
(Chapter~\ref{chap:eval}). The type system ensured that the implementation was
safe and explicit with respect to aliasing, read/write permissions, memory
allocation, re-use and deallocation.

>>>>

I showed that this implementation was \textbf{more memory-efficient} than one
written using a high-level linear-algebra libraries and performed just as
\textbf{predictably} as one written using a low-level linear-algebra library,
enabling a programmer to have the best of both worlds
(Chapter~\ref{chap:eval}). The type system ensured that the implementation was
\textbf{safe and explicit} with respect to aliasing, read/write permissions,
memory allocation, re-use and deallocation.

### 2018-05-27 write-up/introduction.tex
Finish Introduction

\chapter{TO DO: Introduction}

@@

\prechapter{%
}%

\section{Overview of Problem}

\section{Contributions}

>>>>

\chapter{Introduction}

@@

Linear types allow the compiler and programmer to statically keep track of the
resources that an implementation uses, thus offering a promising solution to
resource management. However, they have not made their way into mainstream
programming languages. To demonstrate their usefulness, I implemented an OCaml
library that allows users to learn about, use and become familiar with linear
types, specifically in the context of linear-algebra programs.

The main contributions of this thesis are:

\begin{itemize}

    \item An \textbf{original, usable implementation} of a type system that can express
        aliasing, read/write permissions, memory allocation, re-use and deallocation.

    \item An \textbf{original} demonstration of how that type system can be
        \textbf{applied to the APIs} of linear algebra libraries and the
        \textbf{benefits} of doing so.

    \item Many \textbf{new} examples of how the type system can \textbf{automatically
        check} for common aliasing, read/write permissions, memory allocation,
        re-use and deallocation \textbf{errors} in the context of
        linear-algebra programs.

    \item An \textbf{original} demonstration of how that type system can be
        \textbf{useful} for \textbf{matrix expression compilation}.

    \item \textbf{New and readable implementations} of \textbf{non-trivial}
        linear-algebra programs that \textbf{take advantage} of said type
        system.

    \item A \textbf{new solution} to the \textbf{dichotomy} of
        \textbf{readability}, \textbf{ease of reasoning and safety} of
        high-level linear-algebra libraries versus the
        \textbf{memory-efficiency} of low-level linear-algebra libraries.

    \item A \textbf{new library design} to provide said solution in a way that
        \textbf{integrates well} with existing OCaml code and linear-algebra
        libraries.

\end{itemize}
